### 2017-08-23 sheets/talk-6/sheet-6.tex
Minor typos in sheet-6

\begin{exercise}[Product is unique up-to isomorphism]
  Prove that for every category $\cat{A}$ and every objects $X, Y \in \cat{A}$
  all products of $X$ and $Y$ are isomorphic. Thus we can speak of \emph{the} product of $X$ and $Y$.
\end{exercise}

@@

    Lets reconcider the definition of the \emph{product}:
    For every object $A \in \cat{A}$ and arrows $f_1 \from A \to X, f_2 \from A \to Y$ we get that there exists a unique map
    $\bar{f} \from A \to P$, such that
    \[ \xymatrix{
        &A \ar[ldd]_{f_1} \ar@{.>}[d]|{\bar{f}\vphantom{\bar{\bar{f}}}}
        \ar[rdd]^{f_2}&       \\
                &P \ar[ld]^{p_1} \ar[rd]_{p_2}                  &       \\
        X       &                                               &Y
    } \]
    commutes.
    Now we can instantiate $A$ with $P'$, $f_1$ with $p_1$, $f_2$ with $p_2$. By analogous instantiations we get the commuting diagram
    \[ \xymatrix{
      & P \ar@/_/[ldd]_{p_1} \ar@/^/[rdd]^{p_2} & \\
      & P \ar[ld]^{p_1} \ar@/_/@{.>}[dd]|{\bar{f}} \ar@{.>}[u]|{f} \ar[rd]_{p_2} & \\
      X & & Y \\
      & P' \ar[lu]_{p_1'} \ar@/_/@{.>}[uu]|{\tilde{f}} \ar@{.>}[d]|{f'} \ar[ru]^{p'_2} & \\
      & P' \ar@/^/[luu]^{p'_1} \ar@/_/[ruu]_{p'_2} &
    } \]
    for exactly one $f, f', \tilde{f}, \bar{f}$. With the inner triangles we get:
    \begin{alignat*}{2}
      p_1  \of \tilde{f} &= p'_1 &\qquad p_2  \of \tilde{f} &= p'_2 \\
      p'_1 \of \bar{f}   &= p_1  &       p'_2 \of \bar{f}   &= p_2
    \end{alignat*}
    By substitution we get
    \begin{alignat*}{2}
      p_1   \of (\tilde{f} \of \bar{f}) &= p_1  &\qquad p_2  \of (\tilde{f} \of \bar{f}) &= p_2 \\
      p'_1  \of (\bar{f} \of \tilde{f}) &= p'_1 &       p'_2 \of (\bar{f} \of \tilde{f}) &= p'_2
    \end{alignat*}
    With the outer triangles we get:
    \begin{alignat*}{5}
      p_1  &\;\of&&\; f  &= p_1  &\qquad p_2  &\;\of&\; f  &= p_2 \\
      p'_1 &\;\of&&\; f' &= p'_1 &\qquad p'_2 &\;\of&\; f' &= p'_2
    \end{alignat*}
    Note that $f$ and $f'$ are \emph{unique} and the first equations hold for $f = 1_P$ and $f = \tilde{f} \of \bar{f}$, thus $\tilde{f} \of \bar{f} = 1_P$.
    The second equations holds for $f' = 1_{P'}$ and for $f' = \bar{f} \of \tilde{f}$, thus $\bar{f} \of \tilde{f} = 1_{P'}$.
    Thus $P$ and $P'$ are isomorphic. \qedhere
  \end{proof}
\end{answer}

>>>>

\begin{exercise}[Products are unique up-to isomorphism]
  Prove that for every category $\cat{A}$ and every objects $X, Y \in \cat{A}$
  all products of $X$ and $Y$ are isomorphic. Thus we can speak of \emph{the} product of $X$ and $Y$.
\end{exercise}

@@

    Lets reconsider the definition of the \emph{product}:
    For every object $A \in \cat{A}$ and arrows $f_1 \from A \to X, f_2 \from A \to Y$ we get that there exists a unique map
    $\bar{f} \from A \to P$, such that
    \[ \xymatrix{
        &A \ar[ldd]_{f_1} \ar@{.>}[d]|{\bar{f}\vphantom{\bar{\bar{f}}}}
        \ar[rdd]^{f_2}&       \\
                &P \ar[ld]^{p_1} \ar[rd]_{p_2}                  &       \\
        X       &                                               &Y
    } \]
    commutes.
    Now we can instantiate $A$ with $P'$, $f_1$ with $p_1$, $f_2$ with $p_2$. By analogous instantiations we get the commuting diagram
    \[ \xymatrix{
      & P \ar@/_/[ldd]_{p_1} \ar@/^/[rdd]^{p_2} & \\
      & P \ar[ld]^{p_1} \ar@/_/@{.>}[dd]|{\bar{f}} \ar@{.>}[u]|{f} \ar[rd]_{p_2} & \\
      X & & Y \\
      & P' \ar[lu]_{p_1'} \ar@/_/@{.>}[uu]|{\tilde{f}} \ar@{.>}[d]|{f'} \ar[ru]^{p'_2} & \\
      & P' \ar@/^/[luu]^{p'_1} \ar@/_/[ruu]_{p'_2} &
    } \]
    for exactly one $f, f', \tilde{f}, \bar{f}$. With the inner triangles we get:
    \begin{alignat*}{2}
      p_1  \of \tilde{f} &= p'_1 &\qquad p_2  \of \tilde{f} &= p'_2 \\
      p'_1 \of \bar{f}   &= p_1  &       p'_2 \of \bar{f}   &= p_2
    \end{alignat*}
    By substitution we get
    \begin{alignat*}{2}
      p_1   \of (\tilde{f} \of \bar{f}) &= p_1  &\qquad p_2  \of (\tilde{f} \of \bar{f}) &= p_2 \\
      p'_1  \of (\bar{f} \of \tilde{f}) &= p'_1 &       p'_2 \of (\bar{f} \of \tilde{f}) &= p'_2
    \end{alignat*}
    With the outer triangles we get:
    \begin{alignat*}{5}
      p_1  &\;\of&&\; f  &= p_1  &\qquad p_2  &\;\of&\; f  &= p_2 \\
      p'_1 &\;\of&&\; f' &= p'_1 &\qquad p'_2 &\;\of&\; f' &= p'_2
    \end{alignat*}
    Note that $f$ and $f'$ are \emph{unique} and the first equations hold for $f = 1_P$ and $f = \tilde{f} \of \bar{f}$, thus $\tilde{f} \of \bar{f} = 1_P$.
    The second equations holds for $f' = 1_{P'}$ and for $f' = \bar{f} \of \tilde{f}$, thus $\bar{f} \of \tilde{f} = 1_{P'}$.
    Thus $P$ and $P'$ are isomorphic. \qedhere
  \end{proof}
\end{answer}
